---
title: "Antigua IRMA Analysis Inundation Tables"
author: "Richard Heal"
date: "25 March 2020"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#####################################################################
#
# Script to auto-load the tables generated (CSV) and extract data
#
#####################################################################
workingDirectory <- "D:\\Cefas\\A&B\\InundationTables\\AntiguaCSVFiles"
setwd(workingDirectory)

# Get the libraries needed
library(kableExtra)
library(data.table)

```

# Antigua Impact Tables

This document records the processing of data tables generated using the intersection of classified run up water rasters with elements on the islands such as infrastructure, transport and conserved areas.

The data is taken from the automatically processed data files that is present as csv file tables showing the intersection between features and the gridcode associated with them.<p style = "color:red"> At present all grid code values are used but this could be easily altered to reflect bridge heights etc. </p>


```{r Load in the data, echo=FALSE, warning=FALSE, message=FALSE}
# Data is present as a single set of csv files showing the intersection between the classified inundation layer and the features

# Data is across 13 data tables
# airport_facilities = point layer = number affected
# airports = polygon = area affected
# boreholes = points
# bridges = line
# cellTowers = point
options(knitr.kable.NA = '')
TableStems <- c("Antigua_InundationTable_ADM_ATG_Landmass_2005_84",
                "Antigua_InundationTable_HDR_ATG_Waterbodies_2019_84",
                "Antigua_InundationTable_INF_ATG_AccessRoad_APUA",
                "Antigua_InundationTable_INF_ATG_Airports_hotosm",
                "Antigua_InundationTable_INF_ATG_APUA_ElectricityWires",
                "Antigua_InundationTable_INF_ATG_APUA_Substations",
                "Antigua_InundationTable_INF_ATG_Buildings_2010_84",
                "Antigua_InundationTable_INF_ATG_BusRoutes_2019_84",
                "Antigua_InundationTable_INF_ATG_DamsReservoirs_APUA",
                "Antigua_InundationTable_INF_ATG_EducationFacility",
                "Antigua_InundationTable_INF_ATG_EVCharging_2019_84",
                "Antigua_InundationTable_INF_ATG_FireStation",
                "Antigua_InundationTable_INF_ATG_GasStations_2016_84",
                "Antigua_InundationTable_INF_ATG_PoliceFacilities",
                "Antigua_InundationTable_INF_ATG_PumpingStations_APUA",
                "Antigua_InundationTable_INF_ATG_ReligiousCentres",
                "Antigua_InundationTable_INF_ATG_SeaPorts_hotosm",
                "Antigua_InundationTable_INF_ATG_WaterPipelines_APUA",
                "Antigua_InundationTable_INF_ATG_WaterTanks_APUA",
                "Antigua_InundationTable_INF_ATG_WaterTreatmentPlant_APUA",
                "Antigua_InundationTable_INF_ATG_Wells_APUA",
                "Antigua_InundationTable_PRT_ATG_BPNP_2019_84",
                "Antigua_InundationTable_PRT_ATG_DevilsBridge_2010_84",
                "Antigua_InundationTable_PRT_ATG_FortBarrington_2010_84",
                "Antigua_InundationTable_PRT_ATG_GreenCastleHill_2010_84",
                "Antigua_InundationTable_PRT_ATG_NelsonsDockyard_2010_84",
                "Antigua_InundationTable_PRT_ATG_SMMA_2019_84",
                "Antigua_InundationTable_SOC_ATG_Clinics_2016_84",
                "Antigua_InundationTable_SOC_ATG_CulturalHeritage_2018_84",
                "Antigua_InundationTable_SOC_ATG_EmergencyShelters_2019_84",
                "Antigua_InundationTable_SOC_ATG_Schools_2017_84",
                "Antigua_InundationTable_TER_ATG_KeyBiodiversityAreas_2020_84",
                "Antigua_InundationTable_TER_ATG_LandCover_2010_84",
                "Antigua_InundationTable_INF_ATG_NamedRoads_2016_84",
                "Antigua_InundationTable_INF_ATG_MedicalFacilities",
                "Antigua_InundationTable_hotosm_atg_buildings_polygons")

# Data will be loaded into a data frame
InundationImpactTable <- data.frame(stringsAsFactors = FALSE)
for (D in 1:length(TableStems)){
        # Get the DataTable from file
        #print(D)
        Data <- read.csv(file = file.path(workingDirectory, paste0(TableStems[D], ".csv")),
                         stringsAsFactors = FALSE)
        # Input data into the dataframe as appropriate
        if (nrow(Data) == 0){
          InundationImpactTable <- rbind(InundationImpactTable, cbind(
                                                            Element = TableStems[D],
                                                            GridCode = NA,
                                                            Area = NA,
                                                            Length = NA,
                                                            NumberID = NA,
                                                            Name = NA), stringsAsFactors = FALSE)
  } else {
    # Strip out the correct data
    if (D == 1){ # Landmass
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$OBJECTID
      NameD = rep(NA, nrow(Data))}
    if (D == 2){ # waterbodies
      AreaD = Data$AREA 
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$WaterBodyID
      NameD = rep(NA, nrow(Data))}
    if (D == 3){ # access roads
      AreaD = rep(NA, nrow(Data))
      LengthD = Data$LENGTH
      NumberIDD = Data$Id
      NameD = rep(NA, nrow(Data))}
    if (D == 4){ # airports
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$aeroway}
    if (D == 5){ # electricity wires
      AreaD = rep(NA, nrow(Data))
      LengthD =  Data$LENGTH
      NumberIDD = Data$ElecWireID
      NameD = rep(NA, nrow(Data))}
    if (D == 6){ # electricity substations
      AreaD = rep(NA, nrow(Data))
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$SubSt_ID
      NameD = Data$Name}
    if (D == 7){  # ALL buildings
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$BldgID
      NameD = Data$FEATURE}
    if (D == 8){ # Bus routes
      AreaD = rep(NA, nrow(Data))
      LengthD = Data$LENGTH
      NumberIDD =  Data$Bus_Route
      NameD = Data$Rou_Name}
    if (D == 9){ # Dams and reservoirs
      AreaD = rep(NA, nrow(Data))
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$DamR_ID
      NameD = Data$TYPE}
    if (D == 10){ # Educational facilities
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$EdBldg_ID
      NameD = Data$Label_Name}
    if (D == 11){ # EV charging points
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$Id
      NameD = Data$Location}
    if (D == 12){ # Firestation
      AreaD = Data$AREA
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$ED_No
      NameD = Data$Label_Name}
    if (D == 13){ # petrol stations
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$OBJECTID
      NameD = Data$Comment}
    if (D == 14){ # Police facilities
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Police_ID
      NameD = Data$Label_Name}  
    if (D == 15){ # pumping stations
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$PumpID
      NameD = Data$LOCATION}
    if (D == 16){ # Religous centres
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$RelCen_ID
      NameD = Data$Label_Name}
    if (D == 17){ # Sea Ports
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$name}
    if (D == 18){ # Water pipes
      AreaD = rep(NA, nrow(Data))
      LengthD = Data$LENGTH
      NumberIDD = Data$PIPE_ID
      NameD = Data$LOCATOIN}
    if (D == 19){ # Water tanks
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$TANK_ID
      NameD = Data$LOCATION}
    if (D == 20){ # Water treatment
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Treat_ID
      NameD = Data$NAME}
    if (D == 21){ # Wells
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$WELL_ID
      NameD = rep(NA, nrow(Data))}
    if (D == 22){ # Protected Area
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$OBJECTID
      NameD = Data$land_use}
    if (D == 23){ # Protected Area - Devils bridge
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$ID
      NameD = Data$CAPTION}
    if (D == 24){ # Protected Area - Fort Barrington
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$ID
      NameD = Data$Name}
    if (D == 25){ # Protected Area - Greencastle
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$ID
      NameD = Data$CAPTION}
    if (D == 26){ # Protected Area - Nelsons Dockyard
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$ID
      NameD = Data$CAPTION}
    if (D == 27){ # Protected Area - New Proposed Protected Area
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$id
      NameD = Data$Place}
    if (D == 28){ # Clinics
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Clinic_ID
      NameD = Data$Name}
    if (D == 29){ # Cultural sites
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Id
      NameD = Data$Theme}
    if (D == 30){ # Emergency shelters
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Emer_ID
      NameD = Data$Type}
    if (D == 31){ # Schools
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Id
      NameD = Data$School}
    if (D == 32){ # Key biodiversity areas
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$SitRecID
      NameD = Data$NatName}
    if (D == 33){ # Land Coverage/use
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$ID
      NameD = Data$TYPE_2010}
    if (D == 34){ # Roads
      AreaD = rep(NA, nrow(Data))
      LengthD = Data$LENGTH
      NumberIDD = Data$OBJECTID
      NameD = Data$ROAD_TYPE_}
    if (D == 35){ # Medical facilities
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$Med_ID
      NameD = Data$Label_Name}
    if (D == 36){ # HoSM buildings
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = paste0(Data$office,"-",Data$building)}
    # Update the table
    InundationImpactTable <- rbind(InundationImpactTable, cbind(
                                                            Element = rep(TableStems[D], nrow(Data)),
                                                            GridCode = Data$gridcode,
                                                            Area = as.numeric(AreaD),
                                                            Length = as.numeric(LengthD),
                                                            NumberID = as.numeric(NumberIDD),
                                                            Name = NameD) , stringsAsFactors = FALSE)
    }
    
}

InundationImpactTable <- setDT(InundationImpactTable)
###################################################################
# Output the data as a series of tables
# 
# Note - need to control the fact that bridges, buildings can be covered more than once so need to
#        unique these, also roads have different classes
#
#####################################################################################################

###########################################################
# Output as kable extra table with data for: 
#       airports            =   area
#       buildings           =   area, number
#       ferry (ports)       =   area, number
#       roads               =   length
#       Watercourses        =   number
###############################################################
Islands <- c("Antigua")
FeatureDataFrame <- data.frame(stringsAsFactors = FALSE)

# And gather for Antigua

# Airports
airports <- sum(InundationImpactTable[Element ==  TableStems[4] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
airportsN <- InundationImpactTable[Element ==  TableStems[4] & !is.na(NumberID),
                                  .N]
# Buildings
buildingN <- nrow(InundationImpactTable[Element ==  TableStems[7] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
buildingAREA <- sum(InundationImpactTable[Element ==  TableStems[7] & !is.na(NumberID), 
                                  sum(as.numeric(Area)) * 0.001 * 0.001, by = .(NumberID)][, 2], na.rm = TRUE)
# Schools and education facilities
schoolsN <- nrow(InundationImpactTable[Element ==  TableStems[31] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
educationFacN <- nrow(InundationImpactTable[Element ==  TableStems[10] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
educationFacAREA <- sum(InundationImpactTable[Element ==  TableStems[10] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# Buildings according to HoSM
buildingN_HOSM <- nrow(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
buildingAREA_HOSM <- sum(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID), 
                                  sum(as.numeric(Area)) * 0.001 * 0.001, by = .(NumberID)]$V1, na.rm = TRUE)
BuildingSchool_N_HOSM <- nrow(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID) &
                                                      (grepl("school", Name)),  
                                  .N, by = .(NumberID)])
BuildingSchool_AREA_HOSM <- sum(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID)
                                                      & (grepl("school", Name)), 
                                  sum(as.numeric(Area)) * 0.001 * 0.001, by = .(NumberID)]$V1, na.rm = TRUE)
BuildingEducation_N_HOSM <- nrow(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID) &
                                                      (grepl("school", Name) | grepl("university", Name) | grepl("educational_institution", Name)),  
                                  .N, by = .(NumberID)])
BuildingEducation_AREA_HOSM <- sum(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID)
                                                      & (grepl("school", Name) | grepl("university", Name) |grepl("educational_institution", Name) ), 
                                  sum(as.numeric(Area)) * 0.001 * 0.001, by = .(NumberID)]$V1, na.rm = TRUE)
BuildingGOV_N_HOSM <- nrow(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID) &
                                                      (grepl("government", Name)),  
                                  .N, by = .(NumberID)])
BuildingGOV_AREA_HOSM <- sum(InundationImpactTable[Element ==  TableStems[36] & !is.na(NumberID)
                                                      & (grepl("government", Name)), 
                                  sum(as.numeric(Area)) * 0.001 * 0.001, by = .(NumberID)]$V1, na.rm = TRUE)

# Ports
portsN <- (InundationImpactTable[Element ==  TableStems[17] & !is.na(NumberID),
                                  .N])
# All roads and road transport
road_ALL_L <- sum(InundationImpactTable[Element ==  TableStems[34] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
road_ALL_N <- nrow(InundationImpactTable[Element ==  TableStems[34]& !is.na(NumberID),
                                  .N, by = NumberID])
road_AccessL <- sum(InundationImpactTable[Element ==  TableStems[3] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
road_AccessN <- nrow(InundationImpactTable[Element ==  TableStems[3] & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
# residential, tertiary and service roads
roadsL_Major <- sum(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name == "ST") & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Major <- nrow(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name == "ST") & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
# tracks and paths
roadsL_Trail <- sum(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name != "ST" &
                                          Name != "AV") & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Trail <- nrow(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name != "ST" &
                                          Name != "AV") & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
# unclassified
roadsL_Minor <- sum(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name == "AV") & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Minor <- nrow(InundationImpactTable[Element ==  TableStems[34] &
                                        (Name == "AV") & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])

road_busRoutesL <- sum(InundationImpactTable[Element ==  TableStems[8] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
road_busRoutesN <- nrow(InundationImpactTable[Element ==  TableStems[8],
                                  .N, by = Name])
road_EV_PointsN <- nrow(InundationImpactTable[Element ==  TableStems[11]& !is.na(NumberID),
                                  .N, by = NumberID])
road_GasStationsN <- nrow(InundationImpactTable[Element ==  TableStems[13]& !is.na(NumberID),
                                  .N, by = NumberID])
# Water facilities
water_TreatmentStations <- nrow(InundationImpactTable[Element ==  TableStems[20]& !is.na(NumberID),
                                    .N, by = NumberID])
water_PumpingStations <- nrow(InundationImpactTable[Element ==  TableStems[15] & !is.na(NumberID),
                                    .N, by = NumberID])
water_PipesL <- sum(InundationImpactTable[Element ==  TableStems[18] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
water_PipesN <- nrow(InundationImpactTable[Element ==  TableStems[18]& !is.na(NumberID),
                                  .N, by = NumberID])
water_TanksN <- nrow(InundationImpactTable[Element ==  TableStems[19]& !is.na(NumberID),
                                  .N, by = NumberID])
water_WellsN <- nrow(InundationImpactTable[Element ==  TableStems[21]& !is.na(NumberID),
                                  .N, by = NumberID])
water_Reservoirs <- nrow(InundationImpactTable[Element ==  TableStems[9]& !is.na(NumberID),
                                  .N, by = NumberID])
water_waterBodiesAREA <- sum(InundationImpactTable[Element ==  TableStems[2] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
water_waterBodiesN <- nrow(InundationImpactTable[Element ==  TableStems[2] & !is.na(NumberID),  
                                  .N, by = NumberID])

# Electricity facilities
Elec_WiresL <- sum(InundationImpactTable[Element ==  TableStems[5] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
Elec_SubSt <- nrow(InundationImpactTable[Element ==  TableStems[6] & !is.na(NumberID),
                                  .N, by = NumberID])

# Emergency services
Emer_PoliceAREA <- sum(InundationImpactTable[Element ==  TableStems[14] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Emer_PoliceN <- nrow(InundationImpactTable[Element ==  TableStems[14] & !is.na(NumberID),  
                                  .N, by = NumberID])
Emer_FireAREA <- sum(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Emer_FireN <- nrow(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID),  
                                  .N, by = NumberID])
Emer_SheltersN <- nrow(InundationImpactTable[Element ==  TableStems[30] & !is.na(NumberID),  
                                  .N, by = NumberID])
Emer_MedicalFacAREA <- sum(InundationImpactTable[Element ==  TableStems[35] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Emer_MedicalFacN <- nrow(InundationImpactTable[Element ==  TableStems[35] & !is.na(NumberID),  
                                  .N, by = NumberID])

# Social facilities
Social_Clinics <- nrow(InundationImpactTable[Element ==  TableStems[28] & !is.na(NumberID),  
                                  .N, by = NumberID])
Social_Heritage <- nrow(InundationImpactTable[Element ==  TableStems[29] & !is.na(NumberID),  
                                  .N, by = NumberID])
Social_ReligiousAREA <- sum(InundationImpactTable[Element ==  TableStems[16] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Social_ReligiousN <- nrow(InundationImpactTable[Element ==  TableStems[16] & !is.na(NumberID),  
                                  .N, by = NumberID])

# Land area and protected sites
Land_TotalAREA <- sum(InundationImpactTable[Element ==  TableStems[1] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_CoverAREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_Cover_Agri_AREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID) &
                                                (grepl("Agriculture", Name)), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_Cover_Sett_AREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID) &
                                                (grepl("Settlement", Name)), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_Cover_Forest_AREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID) &
                                                (grepl("Forest", Name)), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_Cover_Industrial_AREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID) &
                                                (grepl("Industrial", Name)),
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_Cover_Wetland_AREA <- sum(InundationImpactTable[Element ==  TableStems[33] & !is.na(NumberID) &
                                                (grepl("Wetland", Name) |grepl("Water bodies", Name)), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)

Land_BioDivAREA <- sum(InundationImpactTable[Element ==  TableStems[32] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_BPNP_AREA <- sum(InundationImpactTable[Element ==  TableStems[22] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_Devils_AREA <- sum(InundationImpactTable[Element ==  TableStems[23] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_Fort_AREA <- sum(InundationImpactTable[Element ==  TableStems[24] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_Castle_AREA <- sum(InundationImpactTable[Element ==  TableStems[25] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_Nelson_AREA <- sum(InundationImpactTable[Element ==  TableStems[26] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
Land_PRT_SMMA_AREA <- sum(InundationImpactTable[Element ==  TableStems[27] & !is.na(NumberID), 
                                        sum(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)

# Collect up into a data frame FEATURE/AREA/LENGTH/NUMBER
features <- c("Airport Facilities", "Ferry Terminals - Number","Buildings", "Buildings - schools", "Buildings - Education Facilities",  "All Roads", "Access road","Major roads (streets)", "Minor roads (avenues)", "Trails (unclassified)", "Bus Routes", "EV Charge Points", "Gas Stations","Electricity Wires", "Electricity Substations", "Police", "Fire Brigade", "Emergency Shelters", "Medical Facilities", "Clinics", "Heritage", "Religous Centres", "Water bodies", "Treatment Plants", "Pumping Stations", "Tanks", "Reservoirs", "Wells", "Pipes", "Total Area", "Land Coverage Area (Total)", "Land Coverage Area (Agriculture)",  "Land Coverage Area (Settlement)","Land Coverage Area (Forest)","Land Coverage Area (Industrial)","Land Coverage Area (Wetland)","Protect Area - BPNP", "Protect Area - Devils Bridge", "Protect Area - Fort Barrington", "Protect Area - Greencastle Hill", "Protect Area - Nelson Dockyard", "Protect Area - SMMA", "Key Biodiversity Sites", "HOSM - All", "HOSM - Schools", "HOSM - Education", "HOSM - Government")
AreaFactor <- 1000 * 1000 # To convert back to m2
FeatureDataFrame <- rbind(FeatureDataFrame,
      c(features[1], round(airports * AreaFactor, digits = 7), NA, round(airportsN, digits = 2)), # Airport area and number of facilities
      c(features[2], NA, NA, round(portsN, digits = 2)), # number of ferry terminals
      
      c(features[3], round(buildingAREA * AreaFactor, digits = 7), NA, round(buildingN, digits = 2)), # Number of buildings & area (all)
      c(features[4], NA, NA, round(schoolsN, digits = 2)), # Number of schools
      c(features[5], round(educationFacAREA * AreaFactor, digits = 7), NA, round(educationFacN, digits = 2)), # number & area of education facilities
      
      c(features[6], NA, round(road_ALL_L, digits = 2), round(road_ALL_N, digits = 2)), # All roads Length and number
      c(features[7], NA, round(road_AccessL, digits = 2), round(road_AccessN, digits = 2)), # Access roads Length
      c(features[8], NA, round(roadsL_Major, digits = 2), round(roadsN_Major, digits = 2)), # Major roads - streets
      c(features[9], NA, round(roadsL_Minor, digits = 2), round(roadsN_Minor, digits = 2)), # Minor roads - avenues
      c(features[10], NA, round(roadsL_Trail, digits = 2), round(roadsN_Trail, digits = 2)), # Trials - unclassified
      
      c(features[11], NA, round(road_busRoutesL, digits = 2), round(road_busRoutesN, digits = 2)), # Bus routes Length and number
      c(features[12], NA, NA, round(road_EV_PointsN, digits = 2)), # Electric vehicle charging points
      c(features[13], NA, NA, round(road_GasStationsN, digits = 2)), # Petrol stations
      
      c(features[14], NA, round(Elec_WiresL, digits = 2), NA), # Electricity wire length
      c(features[15], NA, NA, round(Elec_SubSt, digits = 2)), # Electricity substations
      
      c(features[16], round(Emer_PoliceAREA * AreaFactor, digits = 7), NA, round(Emer_PoliceN, digits = 2)),# Emergency service - police
      c(features[17], round(Emer_FireAREA * AreaFactor, digits = 7), NA, round(Emer_FireN, digits = 2)), # Emergency service - Fire
      c(features[18], NA, NA, round(Emer_SheltersN, digits = 7)),# Emergency service - Shelters
      c(features[19], round(Emer_MedicalFacAREA * AreaFactor, digits = 7), NA, round(Emer_MedicalFacN, digits = 2)), # Emergency service - Medical
      
      c(features[20], NA, NA, round(Social_Clinics, digits = 2)), # Social - Clinics
      c(features[21], NA, NA, round(Social_Heritage, digits = 2)), # Social - Heritage
      c(features[22], round(Social_ReligiousAREA * AreaFactor, digits = 7), NA, round(Social_ReligiousN, digits = 2)),# Social - Religous area and number
      
      c(features[23], round(water_waterBodiesAREA * AreaFactor, digits = 7), NA, round(water_waterBodiesN, digits = 2)),# Water bodies area and number
      c(features[24], NA, NA, round(water_TreatmentStations, digits = 2)),# Treatment plants
      c(features[25], NA, NA, round(water_PumpingStations, digits = 2)),# Pumping stations
      c(features[26], NA, NA, round(water_TanksN, digits = 2)),# Tanks
      c(features[27], NA, NA, round(water_Reservoirs, digits = 2)),# Reservoirs
      c(features[28], NA, NA, round(water_WellsN, digits = 2)),# Wells
      c(features[29], NA, round(water_PipesL, digits = 2), round(water_PipesN, digits = 2)),# Pipes
      
      c(features[30], round(Land_TotalAREA * AreaFactor, digits = 7), NA, NA),# Total Land Area
      c(features[31], round(Land_CoverAREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Total)
      c(features[32], round(Land_Cover_Agri_AREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Agriculture)
      c(features[33], round(Land_Cover_Sett_AREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Settlement)
      c(features[34], round(Land_Cover_Forest_AREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Forest)
      c(features[35], round(Land_Cover_Industrial_AREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Industrial)
      c(features[36], round(Land_Cover_Wetland_AREA * AreaFactor, digits = 7), NA, NA),# Land Coverage Area (Wetland)
    
      c(features[37], round(Land_PRT_BPNP_AREA * AreaFactor, digits = 7), NA, NA), # Protected Areas - BPNP
      c(features[38], round(Land_PRT_Devils_AREA * AreaFactor, digits = 7), NA, NA),# Protected Areas - Devils Bridge
      c(features[39], round(Land_PRT_Fort_AREA * AreaFactor, digits = 7), NA, NA),# Protected Areas - Fort Barrington
      c(features[40], round(Land_PRT_Castle_AREA * AreaFactor, digits = 7), NA, NA),# Protected Areas - Greencastle Hill
      c(features[41], round(Land_PRT_Nelson_AREA * AreaFactor, digits = 7), NA, NA),# Protected Areas - Nelsons Dockyard
      c(features[42], round(Land_PRT_SMMA_AREA * AreaFactor, digits = 7), NA, NA),# Protected Areas - SMMA
      
      c(features[43], round(Land_BioDivAREA * AreaFactor, digits = 7), NA, NA), # Protected Areas - Key Biodiversity Areas
      
      c(features[44], round(buildingN_HOSM * AreaFactor, digits = 7), NA, round(buildingN_HOSM, digits = 2)), # HOSM - all
      c(features[45], round(BuildingSchool_AREA_HOSM * AreaFactor, digits = 7), NA, round(BuildingSchool_N_HOSM, digits = 2)), # Hosm - Schools
      c(features[46], round(BuildingEducation_AREA_HOSM * AreaFactor, digits = 7), NA, round(BuildingEducation_N_HOSM, digits = 2)), # Hosm - Education
      c(features[47], round(BuildingGOV_AREA_HOSM * AreaFactor, digits = 7), NA, round(BuildingGOV_N_HOSM, digits = 2)) # Hosm - GOVN
          , stringsAsFactors = FALSE)
colnames(FeatureDataFrame) <- c("Feature", "Area", "Length", "Number")


##############################################################
# Tables
##############################################################

library(kableExtra)
Table1 <- knitr::kable(FeatureDataFrame,
                       col.names = c("Feature", "Area (m^2^)", "Length (km)", "Number")) %>%
    pack_rows("Air and Sea Travel", 1, 2) %>%
    pack_rows("Buildings", 3, 5) %>%
    pack_rows("Roads", 6,13) %>%
    pack_rows("Electricity", 14,15) %>%
    pack_rows("Emergency Facilities", 16,19) %>%
    pack_rows("Social Facilities", 20,22) %>%
    pack_rows("Water facilities", 23,29) %>%
    pack_rows("Land Coverage", 30,37) %>%
    pack_rows("Protected Areas", 38,42) %>%
    pack_rows("Key Biodiversity Areas", 43,43) %>%
  pack_rows("Humanitarian Open Street Map", 44,46) %>%
   kable_styling(bootstrap_options = c("striped", "hover"))
```

### Table showing the impact of the inundation caused by the IRMA Storm Surge

Below is the table of the impact caused by IRMA's storm surge on features on Antigua This is the impact of having some inundation (>0m).

`r Table1`
