---
title: "Barbuda IRMA Analysis Inundation Tables"
author: "Richard Heal"
date: "25 March 2020"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#####################################################################
#
# Script to auto-load the tables generated (CSV) and extract data
#
#####################################################################
workingDirectory <- "D:\\Cefas\\A&B\\InundationTables\\BarbudaCSVFiles"
setwd(workingDirectory)

# Get the libraries needed
library(kableExtra)
library(data.table)

```

# Barbuda Impact Tables

This document records the processing of data tables generated using the intersection of classified run up water rasters with elements on the islands such as infrastructure, transport and conserved areas.

The data is taken from the automatically processed data files that is present as csv file tables showing the intersection between features and the gridcode associated with them.<p style = "color:red"> At present all grid code values are used but this could be easily altered to reflect bridge heights etc. </p>


```{r Load in the data, echo=FALSE, warning=FALSE, message=FALSE}
# Data is present as a single set of csv files showing the intersection between the classified inundation layer and the features

# Data is across 13 data tables
options(knitr.kable.NA = '')
TableStems <- c("Barbuda_InundationTable_INF_BBQ_Roads_2020_84",
                "Barbuda_InundationTable_INF_BBQ_Helipads_hotosm",
                "Barbuda_InundationTable_INF_BBQ_FerryTerminal_polygon_hotosm",
                "Barbuda_InundationTable_INF_BBQ_FerryTerminal_point_hotosm",
                "Barbuda_InundationTable_INF_BBQ_Buildings_schools_hotosm",
                "Barbuda_InundationTable_INF_BBQ_Buildings_govt_hotosm",
                "Barbuda_InundationTable_INF_BBQ_Buildings_ALL_hotosm",
                "Barbuda_InundationTable_INF_BBQ_Airports_hotosm",
                "Barbuda_InundationTable_HDR_BBQ_Waterbodies_polygon_hotosm",
                "Barbuda_InundationTable_HDR_BBQ_Lagoons_2019_84",
                "Barbuda_InundationTable_SOC_BBQ_CulturalHeritage_2018_84",
                "Barbuda_InundationTable_PRT_BBQ_Sanctuary_2013_84",
                "Barbuda_InundationTable_TER_BBQ_KeyBiodiversityAreas_2020_84"
                )

# Data will be loaded into a data frame
InundationImpactTable <- data.frame(stringsAsFactors = FALSE)
for (D in 1:length(TableStems)){
        # Get the DataTable from file
        #print(D)
        Data <- read.csv(file = file.path(workingDirectory, paste0(TableStems[D], ".csv")),
                         stringsAsFactors = FALSE)
        # Input data into the dataframe as appropriate
        if (nrow(Data) == 0){
          InundationImpactTable <- rbind(InundationImpactTable, cbind(
                                                            Element = TableStems[D],
                                                            GridCode = NA,
                                                            Area = NA,
                                                            Length = NA,
                                                            NumberID = NA,
                                                            Name = NA), stringsAsFactors = FALSE)
  } else {
    # Strip out the correct data
    if (D == 1){ # Roads
      AreaD = rep(NA, nrow(Data))
      LengthD = Data$LENGTH
      NumberIDD = Data$ID
      NameD = Data$type}
    if (D == 2){ # helipads
      AreaD = Data$AREA 
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$osm_id
      NameD = rep(NA, nrow(Data))}
    if (D == 3){ # Ferry terminal polygons
      AreaD = Data$AREA
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$amenity}
    if (D == 4){ # Ferry terminal points
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$amenity}
    if (D == 5){ # Buildings schools
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$osm_id
      NameD = rep(NA, nrow(Data))}
    if (D == 6){ # Government buildings
      AreaD = Data$AREA
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$name}
    if (D == 7){  # ALL buildings
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = Data$building}
    if (D == 8){ # Airports
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD =  Data$osm_id
      NameD = Data$name}
    if (D == 9){ # waterbodies
      AreaD = Data$AREA
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$osm_id
      NameD = paste0(Data$natural, "-", Data$water)}
    if (D == 10){ # lagoons
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$OBJECTID
      NameD = Data$Name}
    if (D == 11){ # cultural heritage
      AreaD = rep(NA, nrow(Data))
      LengthD = rep(NA, nrow(Data)) 
      NumberIDD = Data$Id
      NameD = Data$Site}
    if (D == 12){ # sanctuary
      AreaD = Data$AREA
      LengthD =  rep(NA, nrow(Data))
      NumberIDD = Data$SC_ID
      NameD = Data$NAME}
    if (D == 13){ # key biodiversity areas
      AreaD = Data$AREA
      LengthD = rep(NA, nrow(Data))
      NumberIDD = Data$SitRecID
      NameD = Data$NatName}
  # Update the table
    InundationImpactTable <- rbind(InundationImpactTable, cbind(
                                                            Element = rep(TableStems[D], nrow(Data)),
                                                            GridCode = Data$gridcode,
                                                            Area = as.numeric(AreaD),
                                                            Length = as.numeric(LengthD),
                                                            NumberID = as.numeric(NumberIDD),
                                                            Name = NameD) , stringsAsFactors = FALSE)
    }
    
}

InundationImpactTable <- setDT(InundationImpactTable)
###################################################################
# Output the data as a series of tables
# 
# Note - need to control the fact that bridges, buildings can be covered more than once so need to
#        unique these, also roads have different classes
#
#####################################################################################################

###########################################################
# Output as kable extra table with data for: 
#       airports            =   area
#       buildings           =   area, number
#       ferry (ports)       =   area, number
#       roads               =   length
#       Watercourses        =   number
###############################################################
Islands <- c("Barbuda")
FeatureDataFrame <- data.frame(stringsAsFactors = FALSE)

# And gather for Barbuda
airports <- sum(InundationImpactTable[Element ==  TableStems[8] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
airportsN <- nrow(InundationImpactTable[Element ==  TableStems[8] & !is.na(NumberID),
                                  .N, by = NumberID])
buildingN <- nrow(InundationImpactTable[Element ==  TableStems[7] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
buildingAREA <- sum(InundationImpactTable[Element ==  TableStems[7] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
schoolsN <- nrow(InundationImpactTable[Element ==  TableStems[5] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])
governmentBldgN <- nrow(InundationImpactTable[Element ==  TableStems[6] & !is.na(NumberID),  
                                  .N, by = .(NumberID)])

helipadsAREA <- sum(InundationImpactTable[Element ==  TableStems[2] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
helipadsN <- nrow(InundationImpactTable[Element ==  TableStems[2] & !is.na(NumberID),
                                  .N, by = NumberID])
portsN <- nrow(InundationImpactTable[Element ==  TableStems[4] & !is.na(NumberID),
                                  .N, by = NumberID])
portsAREA <- sum(InundationImpactTable[Element ==  TableStems[3] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# All roads
roadsL_ALL <- sum(InundationImpactTable[Element ==  TableStems[1] & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_ALL <- nrow(InundationImpactTable[Element ==  TableStems[1] & !is.na(NumberID),
                                       .N, by = NumberID])
# residential, tertiary and service roads
roadsL_Major <- sum(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "residential" |
                                          Name == "tertiary" |
                                          Name == "service") & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Major <- nrow(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "residential" |
                                          Name == "tertiary" |
                                          Name == "service") & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
# tracks and paths
roadsL_Trail <- sum(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "track" |
                                          Name == "path" | is.na(Name)) & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Trail <- nrow(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "track" |
                                          Name == "path"| is.na(Name)) & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
# unclassified
roadsL_Minor <- sum(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "unclassified") & !is.na(NumberID), 
                                        max(as.numeric(Length)* 0.001), 
                                        by = NumberID]$V1)
roadsN_Minor <- nrow(InundationImpactTable[Element ==  TableStems[1] &
                                        (Name == "unclassified") & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])

# Water courses are split to ponds, reservoirs and lagoons (with empty field which is standing water)
watercourse_ALL <- sum(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
watercourse_ALL_N <- nrow(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID), 
                                        .N, 
                                        by = NumberID])
watercourse_Ponds <- sum(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID) &
                                             ((grepl("water", Name) & grepl("pond", Name)) |
                                             ( grepl("water- ", Name))), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
watercourse_PondsN <- nrow(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID) &
                                             ((grepl("water", Name) & grepl("pond", Name)) |
                                             ( grepl("water- ", Name))), 
                                        .N, 
                                        by = NumberID])
watercourse_Reservoirs <- sum(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID) &
                                             (grepl("water", Name) & grepl("reservoir", Name)), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
watercourse_Lagoons <- sum(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID) &
                                             (grepl("water", Name) & grepl("lagoon", Name)) , 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
watercourse_Wetlands <- sum(InundationImpactTable[Element ==  TableStems[9] & !is.na(NumberID) &
                                             (grepl("wetland", Name)) , 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# Lagoon layer - 2 lagoons - Codrington and one to the north (NAME?)
lagoons_Codrington <- sum(InundationImpactTable[Element ==  TableStems[10] & !is.na(NumberID) &
                                             (grepl("Codrington", Name)), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
lagoons_Other <- sum(InundationImpactTable[Element ==  TableStems[10] & !is.na(NumberID) &
                                             (!grepl("Codrington", Name)) , 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# Protected areas - Lagoon, Goat_Island and Two_foot bay
ProtectedAreas_ALL <- sum(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
ProtectedAreas_GoatIsland <- sum(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID) &
                                                     grepl("GOAT_ISLAND", Name), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
ProtectedAreas_TwoFootBay <- sum(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID) &
                                                     grepl("TWO_FOOT_BAY", Name), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
ProtectedAreas_Lagoon <- sum(InundationImpactTable[Element ==  TableStems[12] & !is.na(NumberID) &
                                                     grepl("LAGOON_SANCTUARY", Name), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# Key biodiversity areas - only 1 area
Biodiversity_ALL <- sum(InundationImpactTable[Element ==  TableStems[13] & !is.na(NumberID), 
                                        max(as.numeric(Area)* 0.001 * 0.001), 
                                        by = NumberID]$V1)
# Cultural heritage
CulturalSitesN <- nrow(InundationImpactTable[Element ==  TableStems[11] & !is.na(NumberID),
                                  .N, by = NumberID])

# Collect up into a data frame FEATURE/AREA/LENGTH/NUMBER
features <- c("Airport Facilities", "Helipads", "Buildings", "Buildings - schools", "Buildings - government", "Ferry Terminals", "All Roads", "Major roads", "Minor roads", "Trail roads", "All water resources","Ponds and Standing Water", "Reservoirs", "Lagoons", "Wetlands", "Area of Codrington Lagoon", "Area of Other lagoon", "Protected Area - All", "Protected Area - Codrington Lagoon", "Protected Area - Goat Island", "Protected Area - Two Foot Bay", "Key Biodiversity Areas", "Number of Cultural Sites")
AreaFactor <- 1000 * 1000 # To convert back to m2
FeatureDataFrame <- rbind(FeatureDataFrame,
      c(features[1], round(airports * AreaFactor, digits = 2), NA, round(airportsN, digits = 2)), # Airport area
      c(features[2], round(helipadsAREA * AreaFactor, digits = 7), NA, round(helipadsN, digits = 2)), # Helipads area & number
      c(features[3], round(buildingAREA * AreaFactor, digits = 7), NA, round(buildingN, digits = 2)), # Number & area of buildings (all)
      c(features[4], NA, NA, round(schoolsN, digits = 2)), # Number of schools
      c(features[5], NA, NA, round(governmentBldgN, digits = 2)), # number of government buildings
      c(features[6], round(portsAREA * AreaFactor, digits = 7), NA, round(portsN, digits = 2)), # area/number of ferry terminals
      c(features[7], NA, round(roadsL_ALL, digits = 2), round(roadsN_ALL, digits = 2)), # All roads
      c(features[8], NA, round(roadsL_Major, digits = 2), round(roadsN_Major, digits = 2)), # Major roads
      c(features[9], NA, round(roadsL_Minor, digits = 2), round(roadsN_Minor, digits = 2)), # Minor roads
      c(features[10], NA, round(roadsL_Trail, digits = 2), round(roadsN_Trail, digits = 2)), # Tracks
      c(features[11], round(watercourse_ALL * AreaFactor, digits = 2), NA, round(watercourse_ALL_N, digits = 2)), # All watercourses
      c(features[12], round(watercourse_Ponds * AreaFactor, digits = 2), NA, round(watercourse_PondsN, digits = 2)), # Ponds/standing water
      c(features[13], round(watercourse_Reservoirs * AreaFactor, digits = 2), NA, NA), # reservoirs
      c(features[14], round(watercourse_Lagoons * AreaFactor, digits = 2), NA, NA), # lagoons
      c(features[15], round(watercourse_Wetlands, digits = 2), NA, NA), # wetlands
      c(features[16], round(lagoons_Codrington * AreaFactor, digits = 2), NA, NA), # Cordrington lagoon
      c(features[17], round(lagoons_Other * AreaFactor, digits = 2), NA, NA), # other lagoon
      c(features[18], round(ProtectedAreas_ALL * AreaFactor, digits = 2), NA, NA), # Protected areas - All
      c(features[19], round(ProtectedAreas_Lagoon * AreaFactor, digits = 2), NA, NA), # Protected areas - Codrington
      c(features[20], round(ProtectedAreas_GoatIsland * AreaFactor, digits = 2), NA, NA), # Protected areas - Goat Island
      c(features[21], round(ProtectedAreas_TwoFootBay * AreaFactor, digits = 2), NA, NA), # Protected areas - Two foot bay
      c(features[22], round(Biodiversity_ALL * AreaFactor, digits = 2), NA, NA), # Key biodiversity area
      c(features[23], NA, NA, round(CulturalSitesN, digits = 2)) # Number of recognised cultural sites
          , stringsAsFactors = FALSE)
colnames(FeatureDataFrame) <- c("Feature", "Area", "Length", "Number")


##############################################################
# Tables
##############################################################

library(kableExtra)
Table1 <- knitr::kable(FeatureDataFrame,
                       col.names = c("Feature", "Area (m^2^)", "Length (km)", "Number")) %>%
   kable_styling(bootstrap_options = c("striped", "hover"))
```

### Table showing the impact of the inundation caused by the IRMA Storm Surge

Below is the table of the impact caused by IRMA's storm surge on features on Barbuda. This is the impact of having some inundation (>0m).

`r Table1`
